Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
comments (restuctures section)

### take -> take
```{r SR taken}
SR <- list()

@@

### fail -> fail
```{r SR PF}
SR$PF <- sequences$PF %>%

@@

### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

@@

### not take -> fail
```{r SR TPF, eval = FALSE}

@@

### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%

>>>>

}
```
###Apply Functions
We apply make_SR to get different types of sequential rules:
#### take -> take
```{r SR taken}
SR <- list()

@@

#### fail -> fail
```{r SR PF}
SR$PF <- sequences$PF %>%

@@

#### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

@@

#### not take -> fail
```{r SR TPF, eval = FALSE}

@@

#### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%
